### 2017-05-29 doc/categories.tex
Changed figures.

\begin{figure*}[t]
\hspace*{-0.5in}
\setlength{\tabcolsep}{0.01pt}
    \begin{tabular}{cccc}
    \includegraphics[scale=0.14]{new_omission_examples/textual1} &
    \includegraphics[scale=0.14]{new_omission_examples/visual1} &
    \includegraphics[scale=0.33]{new_omission_examples/img1} & 
    \includegraphics[scale=0.28]{new_omission_examples/img1_omit} \\
    \includegraphics[scale=0.16]{new_omission_examples/textual2} &
    \includegraphics[scale=0.16]{new_omission_examples/visual2} &
    \includegraphics[scale=0.28]{new_omission_examples/img2} & 
    \includegraphics[scale=0.30]{new_omission_examples/img2_omit}
    \end{tabular}
    \caption{The omission scores of {\sc Visual} and {\sc Textual} for two example sentences, 
and the best retrieved images for the original sentence (left) and the sentence with the most 
important word removed (right). 
%Top row example caption is {\it a bottle next to a windowsill with
%  light coming through},  bottom row: {\it a train on a track next to
%  many bushes}.
}
    \label{fig:omissionex}
\end{figure*}

>>>>

% \begin{figure*}[t]
% \hspace*{-0.5in}
% \setlength{\tabcolsep}{0.01pt}
%     \begin{tabular}{cccc}
%     \includegraphics[scale=0.14]{new_omission_examples/textual1} &
%     \includegraphics[scale=0.14]{new_omission_examples/visual1} &
%     \includegraphics[scale=0.33]{new_omission_examples/img1} & 
%     \includegraphics[scale=0.28]{new_omission_examples/img1_omit} \\
%     \includegraphics[scale=0.16]{new_omission_examples/textual2} &
%     \includegraphics[scale=0.16]{new_omission_examples/visual2} &
%     \includegraphics[scale=0.28]{new_omission_examples/img2} & 
%     \includegraphics[scale=0.30]{new_omission_examples/img2_omit}
%     \end{tabular}
%     \caption{The omission scores of {\sc Visual} and {\sc Textual} for two example sentences, 
% and the best retrieved images for the original sentence (left) and the sentence with the most 
% important word removed (right). 
% %Top row example caption is {\it a bottle next to a windowsill with
% %  light coming through},  bottom row: {\it a train on a track next to
% %  many bushes}.
% }
%     \label{fig:omissionex}
% \end{figure*}

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.5]{omissionex.pdf}
  \caption{Omission scores for an example sentence for {\sc
      LM} and the two pathways, {\sc Textual} and {\sc Visual}, of
    {\sc Imaginet.}}
  \label{fig:omissionex}
\end{figure*}

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.25]{85826.jpg}
  \includegraphics[scale=0.25]{60596.jpg}
  \caption{Images retrieved for an example sentence (left) and the version of
    it with the  second word omitted (right).}
  \label{fig:omissionexpic}
\end{figure*}
